Grove: A Convergent Collaborative Structure-Editor Calculus

### 2020-09-22 grove-paper.tex
Create \Plus and \Minus commands for outlined plus and minus symbols (Michael D. Adams)

%% Packages
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{semantic}
\let\colonapprox\undefined % Avoid redefinition error in `colonequals`
\let\colonsim\undefined % Avoid redefinition error in `colonequals`
\usepackage{colonequals}
\usepackage{mathpartir}
\usepackage{stmaryrd}

@@

@@

Each edge, $\e = (u, v_s, p, v_t)$, has a unique name, $u \in \U$, and connects the child position $p$ of a source vertex $v_s$ to a target vertex $v_t$.
The state of each edge, $\e$, is determined by the corresponding edge state, $\G(\e) \in \Sigma = \{ \bot, +, - \}$. 
If $\G(\e) = \bot$, then $\e$ does not yet exist.
If $\G(\e)$ is $\mathbf{+}$, the edge has been created.
If $\G(\e)$ is -, the edge has been destroyed.
The total ordering $\bot \sqsubseteq \mathbb{+} \sqsubseteq -$ forms a lattice over $\Sigma$.

>>>>

%% Packages
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{semantic}
\let\colonapprox\undefined % Avoid redefinition error in `colonequals`
\let\colonsim\undefined % Avoid redefinition error in `colonequals`
\usepackage{colonequals}
\usepackage{mathpartir}
\usepackage{stmaryrd}
\usepackage{fontawesome}

@@

% Define outline versions of + and -
\def\outlinepad{0.4pt}
\def\outlinestroke{0.4pt}
\newcommand{\Plus}{\mathord{
\begin{tikzpicture}[anchor=base, baseline]
%\node at (0,0) {+};
\path[draw, line width=\outlinestroke]
   ( 0.333em+\outlinestroke/2+\outlinepad,  0.270em+\outlinestroke/2+\outlinepad)
 --( 0.333em+\outlinestroke/2+\outlinepad,  0.229em-\outlinestroke/2-\outlinepad)
 --( 0.021em+\outlinestroke/2+\outlinepad,  0.229em-\outlinestroke/2-\outlinepad)
 --( 0.021em+\outlinestroke/2+\outlinepad, -0.084em-\outlinestroke/2-\outlinepad)
 --(-0.020em-\outlinestroke/2-\outlinepad, -0.084em-\outlinestroke/2-\outlinepad)
 --(-0.020em-\outlinestroke/2-\outlinepad,  0.229em-\outlinestroke/2-\outlinepad)
 --(-0.333em-\outlinestroke/2-\outlinepad,  0.229em-\outlinestroke/2-\outlinepad)
 --(-0.333em-\outlinestroke/2-\outlinepad,  0.270em+\outlinestroke/2+\outlinepad)
 --(-0.020em-\outlinestroke/2-\outlinepad,  0.270em+\outlinestroke/2+\outlinepad)
 --(-0.020em-\outlinestroke/2-\outlinepad,  0.583em+\outlinestroke/2+\outlinepad)
 --( 0.021em+\outlinestroke/2+\outlinepad,  0.583em+\outlinestroke/2+\outlinepad)
 --( 0.021em+\outlinestroke/2+\outlinepad,  0.270em+\outlinestroke/2+\outlinepad)
 --cycle
 ;
\end{tikzpicture}
}}
\newcommand{\Minus}{\mathord{
\begin{tikzpicture}[anchor=base, baseline]
%\node at (0,0) {$-$};
\path[draw, line width=\outlinestroke]
   ( 0.306em+\outlinestroke/2+\outlinepad,  0.270em+\outlinestroke/2+\outlinepad)
 --( 0.306em+\outlinestroke/2+\outlinepad,  0.229em-\outlinestroke/2-\outlinepad)
 --(-0.306em-\outlinestroke/2-\outlinepad,  0.229em-\outlinestroke/2-\outlinepad)
 --(-0.306em-\outlinestroke/2-\outlinepad,  0.270em+\outlinestroke/2+\outlinepad)
 --cycle
 ;
\end{tikzpicture}
}}

@@

Each edge, $\e = (u, v_s, p, v_t)$, has a unique name, $u \in \U$, and connects the child position $p$ of a source vertex $v_s$ to a target vertex $v_t$.
The state of each edge, $\e$, is determined by the corresponding edge state, $\G(\e) \in \Sigma = \{ \bot, \Plus, \Minus \}$. 
If $\G(\e) = \bot$, then $\e$ does not yet exist.
If $\G(\e)$ is $\mathbf{+}$, the edge has been created.
If $\G(\e)$ is -, the edge has been destroyed.
The total ordering $\bot \sqsubset \Plus \sqsubset \Minus$ forms a lattice over $\Sigma$.
